Manuscript draft

### 2019-09-12 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

The latitudinal gradient in FACF (Figs. 2-3) is driven primarily by temperature-related climate variables, with modification by moisture availability (Figs. 4-5). Because many climate variables co-vary across the latitudinal gradient, climatic drivers affect forest carbon flux on much shorter time scales than can be captured by annual climate summary variables, and both climatic conditions and C flux vary interannually around the long-term means, we would not expect any mean annual climate variable to explain variation in FACF. However, it remains informative to consider these relationships. We find that temperature-related climate variables explain the highest proportion of variability in productivity, and among these, $MAT$ is generally the best predictor--perhaps because site-specific MAT is recorded for the majority of sites in ForC, whereas other variables are extracted from a global database. .... The effects of temperature are modified by moisture availability, ...

[ Regarding seasonality, FACF and climate data lack the temporal resolution required to sort this out. We find no support for the argument that correcting for growing season length improves the explanatory power.]

>>>>

The latitudinal gradient in FACF (Figs. 2-3) is driven primarily by temperature-related climate variables, and secondarily by moisture availability (Figs. 4-5). Because many climate variables co-vary across the latitudinal gradient, because climatic drivers affect forest carbon flux on much shorter time scales than can be captured by annual climate summary variables, and because both climatic conditions and C flux vary intra- and inter-annually around the long-term means, it is not appropriate to attempt to identify any one mean annual climate variable as a mechanistic driver of FACF. However, it remains informative to consider these relationships. We find that temperature-related climate variables ($MAT$, temperature seasonality, ...**LIST**) explain the highest proportion of variability in productivity, and among these, $MAT$ is generally the best predictor--perhaps because site-specific MAT is recorded for the majority of sites in ForC, whereas other variables are extracted from global gridded data products (Table S1**?**). .... The effects of temperature are modified by moisture availability, ...

FACF is reduced by climatic seasonality (Fig. 5e), and productivity is shut down during cold- or dry- dormant seasons. To account for this, a number of analyses seeking to characterize global-scale effects of climate on productivity have examined the relationship of FACF per month of the growing season with growing season climatic conditions (**REFS**). We found that the sort of simple metric needed to define growing season at a global scale was uncertain for temperature and problematic for moisture (**WORK ON THIS**). A temperature-defined growing season length had stong positive correlation with FACF (Fig. 5f), but explained less variation than $MAT$. Dividing FACFs by growing season length to yield FACF per growing season month removed the majority of climate-related variation, supporting the idea that the latitudinal gradient in FACF is attributable more to shorter growing seasons at high latitudes than to inherently lower rates of photosyntheiss or respiration by high-latitude forests *[ Enquist GCB review]*. However, there remained a number of significant correlations with growing season climatic conditions. We conclude that correcting for growing season month does little to improve statistical predictive power. WHile
